% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}

\documentclass[]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
  \usepackage{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
  \usepackage[left=2.5in,bottom=1.25in,top=1.25in,right=1in]{geometry}
  \ifxetex
\usepackage[setpagesize=false, % page size defined by xetex
            unicode=false, % unicode breaks when used with xetex
            xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
bookmarks=true,
pdfauthor={},
pdftitle={My preregistration for CIEE},
colorlinks=true,
citecolor=blue,
urlcolor=blue,
linkcolor=magenta,
pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% Customization for cos_prereg
\usepackage{longtable,booktabs,threeparttable,tabularx}
\linespread{1.5}
\newcounter{question}
\setcounter{question}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\setlength{\droptitle}{-2em}
\title{My preregistration for CIEE}
\pretitle{\begin{changemargin}{-8pc}{0pc} \centering\large Preregistration\\ \Huge}
\posttitle{\end{changemargin}}
  \author{
          First Author\textsuperscript{1},
          Laura Super\textsuperscript{1,2}          \\ \vspace{0.5cm}
              \textsuperscript{1} University of British Columbia\\
              \textsuperscript{2} CIEE Course      }

  \def\affdep{{"", ""}}%
  \def\affcity{{"", ""}}%
  \preauthor{\begin{changemargin}{-8pc}{0pc} \centering\large}
  \postauthor{\end{changemargin}}
\date{28. September 2022}
\predate{\begin{changemargin}{-8pc}{0pc} \centering\large\emph}
\postdate{\end{changemargin}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{14.0pt}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\rhead{\large\textsc{\MakeLowercase{My preregistration}}}



% Title settings
\usepackage{titlesec}
\titleformat{\section}[display]{\bfseries\Large}{\thesection}{}{}[]
\titlespacing{\section}{0pc}{*3}{*1.5}
\titleformat{\subsection}[leftmargin]{\titlerule\bfseries\filleft}{\thesubsection}{.5em}{}
\titlespacing{\subsection}{8pc}{5ex plus .1ex minus .2ex}{1.5pc}


% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi


\begin{document}
\maketitle
\vspace{2pc}


\ifPDFTeX
  \newcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}
\else % if luatex or xetex
  \NewCommandCopy{\oldQuestion}{\Question}
  \renewcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}
\fi



\newcommand\Answer[1]{%
    \noindent
    \textit{Registered response}: #1\par}

\hypertarget{study-information}{%
\section{Study Information}\label{study-information}}

\hypertarget{title}{%
\subsection{Title}\label{title}}

Laura's CIEE Project

My preregistration for CIEE

\hypertarget{description}{%
\subsection{Description}\label{description}}

This is for the CIEE course

\hypertarget{hypotheses}{%
\subsection{Hypotheses}\label{hypotheses}}

These are teaching data Laura Super collected. The experiment tests the
hypothesis that warming and nitrogen will impact plant performance and
the associated microbiome.

\hypertarget{design-plan}{%
\section{Design Plan}\label{design-plan}}

\hypertarget{study-type}{%
\subsection{Study type}\label{study-type}}

\textbf{Experiment}. A researcher randomly assigns treatments to plants
in growth chambers, where nitrogen or water is applied and warming is
applied or no warming.

\hypertarget{blinding}{%
\subsection{Blinding}\label{blinding}}

No blinding is involved in this study.

\hypertarget{study-design}{%
\subsection{Study design}\label{study-design}}

This had a warming x nitrogen design.

\hypertarget{randomization}{%
\subsection{Randomization}\label{randomization}}

Randomized block design within growth chambers

\hypertarget{sampling-plan}{%
\section{Sampling Plan}\label{sampling-plan}}

At the end of the experiment.

\hypertarget{existing-data}{%
\subsection{Existing data}\label{existing-data}}

\textbf{Registration prior to creation of data}. As of the date of
submission of this research plan for preregistration, the data has been
collected.

\textbf{Registration prior to any human observation of the data}. As of
the date of submission, the data exist but have not yet been quantified,
constructed, observed, or reported by anyone - including individuals
that are not associated with the proposed study.

\textbf{Registration prior to accessing the data}. As of the date of
submission, the data exist, but have not been accessed by you or your
collaborators. Commonly, this includes data that has been collected by
another researcher or institution.

\textbf{Registration prior to analysis of the data}. As of the date of
submission, the data exist and you have accessed it, though no analysis
has been conducted related to the research plan (including calculation
of summary statistics).

\textbf{Registration following analysis of the data}. Not applicable
Please see \url{https://cos.io/prereg} for more information.

\hypertarget{explanation-of-existing-data}{%
\subsection{Explanation of existing
data}\label{explanation-of-existing-data}}

Phytobiome data

\hypertarget{data-collection-procedures}{%
\subsection{Data collection
procedures}\label{data-collection-procedures}}

At the end of the experiment

\hypertarget{sample-size}{%
\subsection{Sample size}\label{sample-size}}

See dataset on OSF

\hypertarget{sample-size-rationale}{%
\subsection{Sample size rationale}\label{sample-size-rationale}}

Funding and realism :)!

\hypertarget{stopping-rule}{%
\subsection{Stopping rule}\label{stopping-rule}}

Not applicable

\hypertarget{variables}{%
\section{Variables}\label{variables}}

\hypertarget{manipulated-variables}{%
\subsection{Manipulated variables}\label{manipulated-variables}}

Nitrogen and warming. Also there were three tree species.

\hypertarget{measured-variables}{%
\subsection{Measured variables}\label{measured-variables}}

Height, microbiome, etc.

\hypertarget{indices}{%
\subsection{Indices}\label{indices}}

Think about later :)

\hypertarget{analysis-plan}{%
\section{Analysis Plan}\label{analysis-plan}}

\hypertarget{statistical-models}{%
\subsection{Statistical models}\label{statistical-models}}

Soon!

\hypertarget{transformations}{%
\subsection{Transformations}\label{transformations}}

Hmm\ldots.

\hypertarget{inference-criteria}{%
\subsection{Inference criteria}\label{inference-criteria}}

\hypertarget{data-exclusion}{%
\subsection{Data exclusion}\label{data-exclusion}}

None

\hypertarget{missing-data}{%
\subsection{Missing data}\label{missing-data}}

None

\hypertarget{exploratory-analyses-optional}{%
\subsection{Exploratory analyses
(optional)}\label{exploratory-analyses-optional}}

Not applicable

\hypertarget{other}{%
\section{Other}\label{other}}

\hypertarget{other-optional}{%
\subsection{Other (Optional)}\label{other-optional}}

Not applicable

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{section}{%
\subsection{}\label{section}}

\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}

\noindent

\end{document}
